---
title: "OPTIMMAL_seqtree"
author: "Ignacio Borquez Infante"
date: "2023-05-25"
output: html_document
---

# Directory
```{r}
# Remove all objects from the environment
rm(list = ls())

# Perform garbage collection to free up memory
gc()

options(max.print=10000)
```

# Packages
```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(TraMineR)
library(RColorBrewer)
library(colorspace)
library(TraMineRextras)
library(WeightedCluster)
library(NbClust)
library(cluster)
library(arsenal)
library(texreg)
library(PST)
library(xtable)
library(data.table)
library(hash)
```

# Load ready to use datasets
```{r}
load("disp_data_v2.Rda")
load("pat_data.Rda")
```

# Merge
```{r}
# df_pat and df_disp
df_pat <- select(df_pat,
                 ptid, ptid_p, # IDs
                 age_groups, Gender, race_eth, Education_rec, Employment_rec, Marital, Housing, # Sociodemographics
                 Paying_rec, Criminal, # Risk factors
                 opioid_route, diff_opioid, # Opioid use
                 alcohol, cocaine, cannabis, ampheta, meth, benzo, Tobacco, sum_comor) # Psychiatric comorbidities

# Changing marital status
table(df_pat$Marital)
df_pat$Marital <- as.numeric(df_pat$Marital)
df_pat <- df_pat %>%
  mutate_at(vars("Marital"),
            function(x) car::recode(x, "1:2=1;3=2;4=3;5=9"))

df_pat[c("Marital")] <- lapply(df_pat[c("Marital")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "9"), 
                                 labels = c("Single/Never Married",
                                            "Married",
                                            "Formerly married",
                                            "NR"))

unique_data <- unique_data[, -c(3)] 

df_seq <- merge(unique_data,df_pat,by="ptid_p", all = TRUE) # data merge
```

# Filter for complete cases analysis
```{r}
df_seq$race_eth[df_seq$race_eth == "NR"] <- NA
df_seq$Paying_rec[df_seq$Paying_rec == "NR"] <- NA
df_seq$Marital[df_seq$Marital == "NR"] <- NA
df_seq$Education_rec[df_seq$Education_rec == "NR"] <- NA
df_seq$Employment_rec[df_seq$Employment_rec == "NR"] <- NA
df_seq$Housing[df_seq$Housing == "NR"] <- NA
df_seq$Housing[df_seq$Housing == "Other"] <- NA
df_seq$opioid_route[df_seq$opioid_route == "NR"] <- NA

df_seq$race_eth <- droplevels(df_seq$race_eth)
df_seq$Paying_rec <- droplevels(df_seq$Paying_rec)
df_seq$Marital <- droplevels(df_seq$Marital)
df_seq$Education_rec <- droplevels(df_seq$Education_rec)
df_seq$Employment_rec <- droplevels(df_seq$Employment_rec)
df_seq$Housing <- droplevels(df_seq$Housing)
df_seq$opioid_route <- droplevels(df_seq$opioid_route)
df_seq$sum_comor <- droplevels(df_seq$sum_comor)

# Create a new variable indicating whether there are any missing values in the specified columns
df_seq$missing_indicator <- ifelse(
  complete.cases(df_seq$Gender, df_seq$age_groups, df_seq$race_eth, 
                 df_seq$Paying_rec, df_seq$Marital, df_seq$Education_rec, df_seq$Pop, 
                 df_seq$Employment_rec, df_seq$Housing, df_seq$alcohol, 
                 df_seq$cocaine, df_seq$cannabis, df_seq$meth, df_seq$benzo, 
                 df_seq$opioid_route, df_seq$sum_comor, df_seq$site), 
  0, 1
)

# Filter for complete cases
df_seq_complete <- df_seq[df_seq$missing_indicator == 0, ]
```

# Regression tree - complete cases 
## Filter
```{r}
df_seq_tree <- subset(df_seq, Pop == 1 | Pop == 2)

df_seq_tree <- df_seq_tree %>%
  mutate_at(vars("Pop"),
            function(x) car::recode(x, "1=2;2=1"))

df_seq_tree[c("Pop")] <- lapply(df_seq_tree[c("Pop")], factor,
                                 levels=c("1", 
                                          "2"), 
                                 labels = c("Pre", 
                                            "Post"))
```

## Table missing
```{r eval=FALSE}
# Drop levels
df_seq_tree$opioid_route <- droplevels(df_seq_tree$opioid_route)

# Site as factor
df_seq_tree$site <- as.factor(df_seq_tree$site)

# Total time
df_seq_tree$tot_time <- as.numeric(df_seq_tree$tot_time)
df_seq_tree$tot_time_months <- df_seq_tree$tot_time/30 # In months

# Define Table 1
table_1 <- tableby(missing_indicator ~ site + Gender + age_groups + race_eth + Paying_rec + Marital + Education_rec +
                         Employment_rec + Housing + alcohol + cocaine +
                         cannabis + meth + benzo  + opioid_route + sum_comor,
                   data = df_seq_tree, numeric.stats=c("mean", "sd", "median", "q1q3", "min", "max", "Nmiss", "N"),
                   digits=3, digits.p=3, digits.pct=1)

#Summary with labels
summary(table_1)
```

# Filter
## 1a 
```{r}
df_seq_1a <- subset(df_seq_tree, Pop == "Post")
```

## 1b
```{r}
df_seq_1b <- subset(df_seq_tree, Pop == "Pre")
```

# Sequence analysis
## Takehome 1a
```{r}
#Variables as factors
df_seq_1a[c(8:187)] <- lapply(df_seq_1a[c(8:187)], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "4",
                                          "5"), 
                                 labels = c("In-clinic",
                                            "Weekend/Holiday",
                                            "Take-home",
                                            "Missed dose",
                                            "Censored"))

#Labels for sequences
one.labels <- c("In-clinic",
                "Weekend/Holiday",
                "Take-home",
                "Missed dose",
                "Censored")

#Abbreviations
one.scode <-c('IC',
              'HW',
              'TH',
              'NO',
              'CE')

#Define alphabet
one.alphabet <- c("In-clinic",
                "Weekend/Holiday",
                "Take-home",
                "Missed dose",
                "Censored")

# Defining colors
colors <- c("#8DEAF0", "#4685F0", "#F02286",
            "#E6E6E6", "#FFFFFF")

#Sequence object
tk.seq <- seqdef(df_seq_1a,
                 var = 8:187,
                 left="DEL",
                 states=one.scode,
                 missing = NA,
                 labels = one.labels,
                 cpal=colors,
                 alphabet = one.alphabet,
                 xtstep=30,
                 start=0)
# Legeng
seqlegend(tk.seq, fontsize = 1.5)

# Scale for the graphs
day <-c(0:180)
```

### Graphs 1a
```{r eval=FALSE}
# State distribution plot
png("Output/Takehome/Article/1a_tk_dist.png", width = 1000, height = 500, units = "px")
seqdplot(tk.seq, with.legend = "right", ylab="Proportion", xtlab=day, main = "State distribution plot", border = NA, xlab="Days since first admission")
dev.off()

# State frequency plot
png("Output/Takehome/Article/1a_tk_freq.png", width = 1000, height = 500, units = "px")
seqIplot(tk.seq, with.legend = "right", ylab="Frequency", xtlab=day, main = "", border = NA,
         xlab="Days since first admission",
         sortv = "from.end")
dev.off()

# Site
png("Output/Takehome/Article/1a_site_freq.png", width = 600, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1a$site, with.legend = F, ylab="Frequency", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 9, cols = 1,
         cex.axis=2 , cex.main = 2,
         sortv = "from.end")
dev.off()

# Age groups
png("Output/Takehome/Article/1a_age_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1a$age_groups, with.legend = "right", ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 4, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()

# Housing
png("Output/Takehome/Article/1a_housing_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1a$Housing, with.legend = F, ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 3, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()

# Methamphetamine
png("Output/Takehome/Article/1a_meth_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1a$meth, with.legend = "right", ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 2, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()

# Gender
png("Output/Takehome/Article/1a_gender_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1a$Gender, with.legend = "right", ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 2, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()
```

### Multifactor analysis and regression treee
```{r eval=FALSE}
# Site as factor
df_seq_1a$site <- as.factor(df_seq_1a$site)

# Multifactor discrepancy analysis
tk.mfac = dissmfacw(dist.lcs ~  Gender + age_groups + race_eth + Paying_rec + Marital + Education_rec +
                                Employment_rec + Housing + alcohol + cocaine +
                                cannabis + meth + benzo + opioid_route + sum_comor + site,
                    data = df_seq_1a, 
                    R = 5000)

# Table
tt = data.table(tk.mfac$mfac[order(-tk.mfac$mfac$PseudoR2), ])

# Regression tree
st_tk <- seqtree(tk.seq ~  Gender + site + opioid_route + meth + age_groups + Marital + sum_comor,
                 data = df_seq_1a, 
                 R = 5000, 
                 diss = dist.lcs,
                 weight.permutation = "diss",
                 max.depth = 5,
                 pval = 0.05)

# Plot regression tree (most have Graphviz installed)
seqtreedisplay(st_tk, type = "I", border = NA, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2,
         sortv = "from.end")

seqtreedisplay(st_tk, type = "d", border = NA, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2)

seqtreedisplay(st_tk, type = "mt", border = T, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2)

seqtree2dot(st_tk, filename="mytree", type = "I", border = NA, cex.main = 2, sortv = "from.end") # Regression tree by piece
```

## Takehome 1b
```{r}
df_seq_1b[c(8:187)] <- lapply(df_seq_1b[c(8:187)], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "4",
                                          "5"), 
                                 labels = c("In-clinic",
                                            "Weekend/Holiday",
                                            "Take-home",
                                            "Missed dose",
                                            "Censored"))

#Sequence object
tk.seq <- seqdef(df_seq_1b,
                 var = 8:187,
                 left="DEL",
                 states=one.scode,
                 missing = NA,
                 labels = one.labels,
                 cpal=colors,
                 alphabet = one.alphabet,
                 xtstep=30,
                 start=0)
```

### Graphs 1b
```{r eval=FALSE}
# State distribution plot
png("Output/Takehome/Article/1b_tk_dist.png", width = 1000, height = 500, units = "px")
seqdplot(tk.seq, with.legend = "right", ylab="Proportion", xtlab=day, main = "State distribution plot", border = NA, xlab="Days since first admission")
dev.off()

# State frequency plot
png("Output/Takehome/Article/1b_tk_freq.png", width = 1000, height = 500, units = "px")
seqIplot(tk.seq, with.legend = "right", ylab="Frequency", xtlab=day, main = "", border = NA,
         xlab="Days since first admission",
         sortv = "from.end")
dev.off()

# Site
png("Output/Takehome/Article/1b_site_freq.png", width = 600, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1b$site, with.legend = F, ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 9, cols = 1,
         cex.axis= , cex.main = 2,
         sortv = "from.end")
dev.off()

# Age groups
png("Output/Takehome/Article/1b_age_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1b$age_groups, with.legend = "right", ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 4, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()

# Housing
png("Output/Takehome/Article/1b_housing_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1b$Housing, with.legend = F, ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 3, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()

# Methamphetamine
png("Output/Takehome/Article/1b_meth_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1b$meth, with.legend = "right", ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 2, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()

# Gender
png("Output/Takehome/Article/1b_gender_freq.png", width = 750, height = 1500, units = "px")
seqIplot(tk.seq, group = df_seq_1b$Gender, with.legend = "right", ylab="Proportion", xtlab=day, main = "", border = NA, 
         xlab="Days since first admission",
         use.layout=TRUE, rows = 2, cols = 1,
         cex.axis=1.5 , cex.main = 2,
         sortv = "from.end")
dev.off()
```

### Multifactor analysis and regression treee
```{r eval=FALSE}
# LCS distance matrix
dist.lcs <- seqdist(tk.seq, method="LCS")

# Site as factor
df_seq_1b$site <- as.factor(df_seq_1b$site)

# Multifactor discrepancy analysis
tk.mfac = dissmfacw(dist.lcs ~  Gender + age_groups + race_eth + Paying_rec + Marital + Education_rec +
                                Employment_rec + Housing + alcohol + cocaine +
                                cannabis + meth + benzo + opioid_route + sum_comor + site,
                    data = df_seq_1b, 
                    R = 5000)

# Table
tt = data.table(tk.mfac$mfac[order(-tk.mfac$mfac$PseudoR2), ])

# Regression tree
st_tk <- seqtree(tk.seq ~  site,
                 data = df_seq_1b, 
                 R = 5000, 
                 diss = dist.lcs,
                 weight.permutation = "diss",
                 max.depth = 5,
                 pval = 0.05)

# Plot regression tree
seqtreedisplay(st_tk, type = "I", border = NA, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2,
         sortv = "from.end")

seqtreedisplay(st_tk, type = "d", border = NA, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2)

seqtreedisplay(st_tk, type = "mt", border = T, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2)

seqtree2dot(st_tk, filename="mytree", type = "I", border = NA, cex.main = 2, sortv = "from.end") # Regression tree by piece
```

# Consecutive take-homes
```{r}
# Create a new column to store the count of consecutive "3"
df_seq_tree$consecutive_3 <- 0

# Iterate over each row
for (i in 1:nrow(df_seq_tree)) {
  consecutive_count <- 0
  max_consecutive_count <- 0
  
  # Iterate over each column starting from tk_day1 to tk_day180
  for (j in 8:187) {
    if (df_seq_tree[i, j] == 3) {
      consecutive_count <- consecutive_count + 1
      if (consecutive_count > max_consecutive_count) {
        max_consecutive_count <- consecutive_count
      }
    } else {
      consecutive_count <- 0
    }
  }
  
  # Update the 'consecutive_3' column with the maximum consecutive count
  df_seq_tree$consecutive_3[i] <- max_consecutive_count
}

# Count the maximum number of consecutive "3" by ptid_p
max_consecutive_3 <- aggregate(consecutive_3 ~ ptid_p, df_seq_tree, max)

df_seq_tree <- df_seq_tree[, -c(462)] 

df_seq_tree <- merge(df_seq_tree,max_consecutive_3,by="ptid_p", all = TRUE) # data merge

#df_seq_tree$consecutive_3[is.na(df_seq_tree$count_type3)] <- NA

df_seq_tree <- df_seq_tree %>%
  mutate_at(vars("consecutive_3"),
            function(x) car::recode(x, "0=1;1:6=2;7:13=3;14:117=4;NA=NA"))

a <- table(df_seq_tree$consecutive_3)
round(prop.table(a)*100, 2)

a <- table(df_seq_tree$consecutive_3, useNA = "ifany")
round(prop.table(a)*100, 2)

df_seq_tree[c("consecutive_3")] <- lapply(df_seq_tree[c("consecutive_3")], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "4"), 
                                 labels = c("No take-home",
                                            "1 to 6",
                                            "7 to 13",
                                            "14 or more"))
```

# Tables

## Labels
```{r}
# Creating labels
mylabels <- list(site = "Site",
Gender = "Sex",
age_groups = "Age groups",
race_eth = "Race/Ethnicity",
Paying_rec = "Type of insurance",
Marital = "Marital status",
Education_rec = "Education",
Employment_rec = "Employment",
Housing = "Housing status",
alcohol = "Alcohol use intake",
cocaine = "Cocaine use intake",
cannabis = "Cannabis use intake",
meth = "Methamphetamine use intake",
benzo = "Benzodiazepines use intake",
diff_opioid = "Difference between opioid initiation and current age",
opioid_route = "Route of administration of opioids",
sum_comor = "At least one psychiatric comorbidity",
count_total = "Total number of encounters",
count_type1 = "Number of days in-clinic",
prct_type1 = "Proportion of days in-clinic",
count_type2 = "Number of days weekend/holidays",
prct_type2 = "Proportion of days weekend/holidays",
count_type3 = "Number of days take-home",
prct_type3 = "Proportion of days take-home",
count_type4 = "Number of days missed dose",
prct_type4 = "Proportion of days missed dose",
tot_time_months = "Total months observed",
consecutive_3 = "Maximum consecutive take-home days"
)
```

## Table 1
```{r eval=FALSE}
# Drop levels
df_seq_tree$opioid_route <- droplevels(df_seq_tree$opioid_route)

# Site as factor
df_seq_tree$site <- as.factor(df_seq_tree$site)

# Total time
df_seq_tree$tot_time <- as.numeric(df_seq_tree$tot_time)
df_seq_tree$tot_time_months <- df_seq_tree$tot_time/30 # In months

# Define Table 1
table_1 <- tableby(Pop ~ site + Gender + age_groups + race_eth + Paying_rec + Marital + Education_rec +
                         Employment_rec + Housing + alcohol + cocaine +
                         cannabis + meth + benzo  + opioid_route + sum_comor +  
                         count_total + count_type1 + prct_type1 + count_type2 + prct_type2 + 
                         count_type3 + prct_type3 + count_type4 + prct_type4 + tot_time_months + consecutive_3,
                   data = df_seq_tree, numeric.stats=c("mean", "sd", "median", "q1q3", "min", "max", "Nmiss", "N"),
                   digits=3, digits.p=3, digits.pct=1)

#Summary with labels
summary(table_1, labelTranslations = mylabels)

# Export table 
write2word(table_1, "Table_1.docx", 
           title="Table 1",labelTranslations = mylabels, text=TRUE)
```

# Sequence analysis whole sample
## Takehome
```{r}
df_seq_tree[c(8:187)] <- lapply(df_seq_tree[c(8:187)], factor,
                                 levels=c("1", 
                                          "2",
                                          "3",
                                          "4",
                                          "5"), 
                                 labels = c("In-clinic",
                                            "Weekend/Holiday",
                                            "Take-home",
                                            "Missed dose",
                                            "Censored"))

#Labels for sequences
one.labels <- c("In-clinic",
                "Weekend/Holiday",
                "Take-home",
                "Missed dose",
                "Censored")

#Abbreviations
one.scode <-c('IC',
              'HW',
              'TH',
              'NO',
              'CE')

one.alphabet <- c("In-clinic",
                "Weekend/Holiday",
                "Take-home",
                "Missed dose",
                "Censored")

# Defining colors
colors <- c("#8DEAF0", "#4685F0", "#F02286",
            "#E6E6E6", "#FFFFFF")

#Sequence object
tk.seq <- seqdef(df_seq_tree,
                 var = 8:187,
                 left="DEL",
                 states=one.scode,
                 missing = NA,
                 labels = one.labels,
                 cpal=colors,
                 alphabet = one.alphabet,
                 xtstep=30,
                 start=0)
```

### Dissimilary matrix
```{r}
dist.lcs <- seqdist(tk.seq, method="LCS")
```

### Multifactor analysis
```{r}
df_seq_tree$site <- as.factor(df_seq_tree$site)

tk.mfac = dissmfacw(dist.lcs ~  Gender + age_groups + race_eth + Paying_rec + Marital + Education_rec +
                                Employment_rec + Housing + alcohol + cocaine +
                                cannabis + meth + benzo + opioid_route + sum_comor + site + Pop,
                    data = df_seq_tree, 
                    R = 5000)

tt = data.table(tk.mfac$mfac[order(-tk.mfac$mfac$PseudoR2), ])
```

### Regression tree
```{r}
df_seq_tree$site <- as.factor(df_seq_tree$site)

st_tk <- seqtree(tk.seq ~  Paying_rec + Employment_rec + 
                           Housing + meth + cannabis + Pop + site,
                 data = df_seq_tree, 
                 R = 5000, 
                 diss = dist.lcs,
                 weight.permutation = "diss",
                 max.depth = 5,
                 pval = 0.05)

seqtreedisplay(st_tk, type = "I", border = NA, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2,
         sortv = "from.end", show.tree = T)

seqtreedisplay(st_tk, type = "d", border = NA, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2)

seqtreedisplay(st_tk, type = "mt", border = T, image.format = "png", gvpath = 'C:/Program Files/Graphviz',
               cex.main = 2)

seqtree2dot(st_tk, filename="mytree", type = "I", border = NA, cex.main = 2, sortv = "from.end") # Regression tree by piece
```

# Tables for supplementary
## Site
```{r eval=FALSE}
df_seq_tree$site <- as.factor(df_seq_tree$site)

table_site <- tableby(site ~ prct_type1 + prct_type2 + prct_type3 + prct_type4 + tot_time_months,
                   data = df_seq_tree, numeric.stats=c("mean", "sd", "Nmiss", "N"),
                   digits=3, digits.p=3, digits.pct=1, strata = Pop)
```

## Meth
```{r eval=FALSE}
table_meth <- tableby(meth ~ prct_type1 + prct_type2 + prct_type3 + prct_type4 + tot_time_months,
                   data = df_seq_tree, numeric.stats=c("mean", "sd", "Nmiss", "N"),
                   digits=3, digits.p=3, digits.pct=1, strata = Pop)
```

## Age groups
```{r eval=FALSE}
table_age_groups <- tableby(age_groups ~ prct_type1 + prct_type2 + prct_type3 + prct_type4 + tot_time_months,
                   data = df_seq_tree, numeric.stats=c("mean", "sd", "Nmiss", "N"),
                   digits=3, digits.p=3, digits.pct=1, strata = Pop)
```

## Gender
```{r eval=FALSE}
table_Gender <- tableby(Gender ~ prct_type1 + prct_type2 + prct_type3 + prct_type4 + tot_time_months,
                   data = df_seq_tree, numeric.stats=c("mean", "sd", "Nmiss", "N"),
                   digits=3, digits.p=3, digits.pct=1, strata = Pop)
```

## Housing
```{r eval=FALSE}
table_Housing <- tableby(Housing ~ prct_type1 + prct_type2 + prct_type3 + prct_type4 + tot_time_months,
                   data = df_seq_tree, numeric.stats=c("mean", "sd", "Nmiss", "N"),
                   digits=3, digits.p=3, digits.pct=1, strata = Pop)
```

## Export
```{r}
write2word(table_site, "Table_site.docx", title="Table 1",labelTranslations = mylabels, text=TRUE)
write2word(table_meth, "Table_meth.docx", title="Table 1",labelTranslations = mylabels, text=TRUE)
write2word(table_age_groups, "Table_age.docx", title="Table 1",labelTranslations = mylabels, text=TRUE)
write2word(table_Gender, "Table_Gender.docx", title="Table 1",labelTranslations = mylabels, text=TRUE)
write2word(table_Housing, "Table_Housing.docx", title="Table 1",labelTranslations = mylabels, text=TRUE)
```

